\section{Web Service API}\label{design:web_service}
The web service API was implemented using ASP.NET Web API 2.3\cite{aspnet_webapi}, which is an implementation of the Model-View-Controller architecture.
In the architecture of \projectname{}, the web service is defined as a component of its own (see \Cref{arch:webservice}).

As described in \Cref{webservice:roa}, ROA sets the ground rules for designing the API.
These criteria are therefore upheld by the API.

\input{content/mvc}

\subsection{Resources}\label{webservice:resources}
This section contains the resources designed and implemented in the web service.
Resources in the implementation are objects, containing named properties and sub-resources.
Sub-resources are represented as simple objects, containing only its relative URL.
Each resource is described following this structure:
\begin{itemize}
\item \textbf{URL:} the URL of the resource
\item \textbf{Properties:} a property which can be accessed from this resource
\item \textbf{Resources:} the resource(s) which can be accessed from this resource
\item \textbf{Methods:} HTTP methods which can be used on that resource
\item \textbf{Responses:} HTTP status codes which could be returned by this resource
\end{itemize}

\subsection{The resources implemented:}
% Command for displaying url, properties, and sub-resource of each resource
\newcommand{\resource}[6]{\noindent \fbox{\begin{minipage}{\textwidth}
\begin{multicols}{2}
\begin{description}
\item[URL:]{\texttt{#1}}
\item[Properties:]{\texttt{#2}}
\end{description}
\end{multicols}
\begin{description}
\item[Resources:]{\texttt{#3}}
\end{description}
\begin{multicols}{2}
\begin{description}
\item[Methods:]{\texttt{#4}}
\item[Responses:]{\texttt{#5}}
\end{description}
\end{multicols}
{#6}
\end{minipage}
}\vspace{0.3cm}}

\resource{/}{version}{availablebikes, hotspots, predictions}{GET}{200 OK}
{The root path serves as the entry point for the API.
It has a single property; version, to be used for asserting that the API has changes that implementations should react to.
More importantly, it contains a sub-resource for each main resource.}

\resource{/availablebikes}{count}{List of availablebikes}{GET}{200 OK}
{This resource contains a list of all \texttt{availablebike} resources, along with a count of how many there are.}

\resource{/availablebikes/\{bikeId\}}{latitude, longitude}{}{GET}{200 OK, 404 Not Found}
{This is the actual \texttt{availablebike} resource.
In case a client tries to request a bike that is not available, it will be met with a \texttt{404 Not Found} response.}

\resource{/hotspots}{hotspots}{}{GET}{200 OK}
{This resource returns a list of all the hotspot resources in the system.}

\resource{/hotspots/hotspot}{coordinates}{}{GET}{200 OK, 404 Not Found}
{This resource returns the points the make up the convex hull of a single hotspot.
In case a client tries to request a hotspot that is not available, it will be met with a \texttt{404 Not Found} response.}

\resource{/prediction}{}{}{GET}{200 OK}
{This is the prediction resource.
When a client wants to know when a bike arrives at a hotspot this resource can be used.}

\alexander{Se og vurder om API Kasserne nu er ok.}

