\section{Generating the Average Bike Model} \label{markov:create_model}
Matrices that describe the transition probabilities of Markov chains, should be generated from the GPS locations collected from the bikes in the system.
This process is handled by \Cref{markov:alg:create_model}.
The algorithm takes a set of hotspots $H$ and the set of GPS locations $G$, from which the matrix should be built.
For each hotspot $h \in H$ there exists a departure state $d \in D$.
Additionally, $B$ represents the set of bikes that is being modeled.

It is presumed that $G$ is implemented using a data structure that allows the retrieval of a single element using a chronological ordering.
This will allow us to retrieve the first/last element in the set and to compare elements using the $=$, $<$ and $>$ operators.

\paragraph{Functions}
We let $g \in G$ represent a single GPS location and say that $G(b) \mid b \in B$ represents the set of GPS locations assocaited with bike $b$.
Both $G$ and $G(b)$ can then be seen as ordered sets of GPS locations.

From this we can provide a definition for the function $G(b, d)$ where $d$ is a representation of a date.
Let $G(b) = \{g_0, g_1, \dots, g_n\}$, then we have that:
\begin{equation}
G(b, d) = 
\left\{
  \begin{array}{l l}
    g_0 & \text{if $g_0.date > d$}\\
    g_n & \text{if $g_n.date \leq d$}\\
    g_k & \text{where $g_k.date \leq d \wedge g_{k+1}.date > d$}
  \end{array} \right.
\end{equation}
$L(b)$ represents a collection of $bike \rightarrow state$ references and is used to maintain a list of the last known location of each bike.

\begin{algorithm}
\SetAlgoNoEnd
\textbf{CreateModel($H, G, step$)}\\
Let $M$ be an empty $n \times n$ matrix with $n = 2|H|$ \\
\ForEach{$b \in B$}
	{
	$g \leftarrow G(b).first$\\
	$L(b) \leftarrow
	 \textbf{NearestState}(H, g)$
	}
Let $d \leftarrow G.first.date$\\
Let $l \leftarrow G.last.date$\\
\While{$d \leq l$}
	{
	\ForEach{$b \in B$}
		{
		$g \leftarrow G(b, d)$\\
		$n \leftarrow \textbf{NearestState}(H, g)$\\
		\If{$n \in D \wedge L(b) \in D$}
			{
			$n \leftarrow L(b)$
			}
		\ElseIf{$n \in D \wedge L(b) \in H$}
			{
			$n \leftarrow L(b).departure$
			}
		}
	$d \leftarrow \text{Add}(d, step)$
	}
Normalize $M$\\
\Return{M}
\caption{Creating the model.}
\label{markov:alg:create_model}
\end{algorithm}

\begin{algorithm}
\SetAlgoNoEnd
\textbf{NearestState($H, g$)}\\
$n \leftarrow \textbf{nil}$\\
$mindist = \infty$\\
\ForEach{$h \in H$}
	{
	$d \leftarrow distance(h, g)$\\
	\If{$d < mindist$}
		{
		$n \leftarrow h$\\
		$mindist = d$\\
		}
	}
\If{$\neg contains(n, g)$}
	{
	$n \leftarrow n.departure$
	}
\Return{n}
\caption{Creating the model.}
\label{markov:alg:nearest}
\end{algorithm}