\subsection{Data Loading}\label{arch:data_loading_component}
The data loading component has the responsibility for fetching GPS points and processing them before inserting them into the database.
The component consists of a \texttt{Data Collector}, a \texttt{Location Source}, and a \texttt{Common} layer that contains an interface and data transfer objects.

The parts of this component will be described in this section.
\begin{figure}[h]
\centering
\begin{tikzpicture}[
path/.style={
	->,
	>=stealth
},
every node/.style={font=\sffamily,minimum height=1cm}]

\node[draw,minimum width=3cm,xshift=0.5cm](datacollector){Data Collector};

\node[draw,below=of datacollector](locationsource){Location source};

\node[draw,right=of datacollector, rotate=90,anchor=south,xshift=-1cm,yshift=-0.5cm, minimum width=3cm](common){Common};

\node[above=of datacollector, yshift=-1.2cm,xshift=-0.9cm](dataloading){Data loading};

\draw ($ (dataloading.north west) + (-0.3,0.3) $) rectangle ($ (common.south west)+(0.3,-0.7) $);

\draw[path] (datacollector.south) -- (locationsource.north);

\draw[path] (datacollector.east) -- (common.north);

\draw[path] (locationsource.east) -- (common.north);

\end{tikzpicture}
\caption{The Data Loading Component. The full diagram can be seen on \cref{arch}}
\label{dataloadingcomponent}
\end{figure}

\subsubsection{Common}
The \texttt{Data Loading} component contains interfaces and data transfer objects for the \texttt{Data Loading} component.

The \lstinline!GPSInput! class works as a data transfer object for \lstinline!GPSData! in the \texttt{Model} layer of the \texttt{Business Logic} component.

The \lstinline!IDataSource! interface defines the behaviour of a data source in the system enabling the source to be changed.
The interface can be seen in \cref{idatasourcecode}.

\begin{lstlisting}[language=C,caption=The IDataSource interface,label=idatasourcecode]
public interface IDataSource
{
	GPSInput GetData();
}
\end{lstlisting}

The \lstinline!GetData();! method returns the oldest \lstinline!GPSInput! available if any is available.
If no \lstinline!GPSInput! is available it returns null.

\subsubsection{Data Collector}
The \texttt{Data Loader} works as an independent program that continuously asks the \lstinline!Location Source! for new \lstinline!GPSInput!.
The \lstinline!Location Source! is an implementation of the \lstinline!IDataSource! and the \texttt{Data Loader} can therefore use any source that implements this interface.

\subsubsection{Location Source}\label{design:location_source}
The \texttt{Location Source} contains implementations of the \lstinline!IDataSource! and will therefore contain an implementation of the simulation of bikes.
In the real system an implementation will be made where the data is fetched from the GPS trackers on the bikes instead.

The implementation of the bike simulation will be described in \cref{design:datasimulation}.
 